Simple models of deliberated preference

### 2017-11-02 article.tex
Removed old todos
Intro

\begin{document}
\title{The title}
\author{Olivier Cailloux}
\makeatletter
	\hypersetup{
		pdfsubject={Epistemology},
		pdfkeywords={Decision aiding, Decision making, Argumentation}
	}
\makeatother
\maketitle

@@

\appendix
\section{Todo}
Road map.
\begin{itemize}
	\item P1: $p_a$ is w-a or $p_{¬a}$ is w-a
	\item Define $p_{a}$ is strongly accepted; $p_{¬a}$ is strongly rejected, so that they are equivalent.
	\item P2: $p_a$ is w-a or $p_{¬a}$ is strongly accepted.
\end{itemize}

Other todos.
\begin{itemize}
	\item If $i$ does not consider $\ar$ as supporting $\prop$, it also works: if $\prop$ is not weakly acceptable by default, then any $\ar'$ is considered by $i$ as a better argument than $\ar$ in favor of certain $¬\prop$, and so on. In fact, whether $\emptyset \ibeatse[\prop] \emptyset$ determines whether $\prop$ is weakly supported by default.
	\item I should define $\ar' (□\ibeatse[\prop]) \ar$ as an observable: “Assuming $\ar'$ would survive, do you consider $\ar'$ as leading to certainty of $¬\prop$, even when considering $\ar$?”. It distinguishes our knowledge and the truth: $\ar' (□\ibeatse[\prop]) \ar ⇒ \ar' \ibeatse[\prop] \ar$, thus, implies $¬ (\ar' \nibeatsst[\prop] \ar)$. But out of $¬ (\ar' (□\ibeatse[\prop]) \ar)$, nothing.
	\item Partition (objectively) $\allargs$ (or $\allargs × \alltopic$) into arguments in favor of $\prop, \text{sure}$, $¬\prop, \text{sure}$, and similarly for possible. Use only one rel $\ibeatse$, defined on contradictory arguments only, instead of $\ibeatse[\prop, \text{sure}]$ and others. Define $\ar' \ibeatse[\prop] \ar$ equals no when $¬(\ar' \ileadsto ¬\prop, \text{sure})$, equals $\ibeatse$ for adequate arguments, and equals yes when $¬(\ar \ileadsto \prop, \text{possible})$ and $\ar' \ileadsto ¬\prop, \text{sure}$, with probably some complications needed for the argument $\emptyset$ (and related default attitude towards $\prop$).
\end{itemize}

>>>>

\begin{document}
\title{Simple models of deliberated preference}
\author{Olivier Cailloux \and Yves Meinard}
\makeatletter
	\hypersetup{
		pdfsubject={Epistemology},
		pdfkeywords={Decision aiding, Decision making, Argumentation}
	}
\makeatother
\maketitle

\section{Motivation}
We define the deliberated preference of an individual. We are interested in a context of a choice of a subset of alternatives from a set of possible alternatives given a priori. We define a model of the DP and give conditions and a validation procedure that ensure that what the model claims is in the DP is indeed. We want in particular to allow for the model to be applicable to various individuals that start with different knowledge: the model may use different counter-arguments to convince different individuals.

More in detail. A full-blown proof may be so long that nobody would read it. (That’s why mathematicians do not write their proofs in set-theoretic bare notation.) Hence, shortcuts are taken, which rely on the individual knowing stuff already. More generally, assume you want to convince someone of fact $F$ with a text (we call this an argument), in our case, we want to convince a person that such alternative from the set is a good choice for her. The argument may assume the reader knows already why such or such possible counter-arguments are invalid, and the argument will thus not delve into the details of some points. When shown in interactive mode (our context here), an individual may however question some points (which we call a counter-argument). The argumenter should then be able to provide an answer to the query (a counter-counter-argument).

This article aims at defining such a procedure and conditions of its validity.

@@

\appendix
\section{Todo}
\begin{itemize}
	\item If $i$ does not consider $\ar$ as supporting $\prop$, it also works: if $\prop$ is not weakly acceptable by default, then any $\ar'$ is considered by $i$ as a better argument than $\ar$ in favor of certain $¬\prop$, and so on. In fact, whether $\emptyset \ibeatse[\prop] \emptyset$ determines whether $\prop$ is weakly supported by default.
	\item I should define $\ar' (□\ibeatse[\prop]) \ar$ as an observable: “Assuming $\ar'$ would survive, do you consider $\ar'$ as leading to certainty of $¬\prop$, even when considering $\ar$?”. It distinguishes our knowledge and the truth: $\ar' (□\ibeatse[\prop]) \ar ⇒ \ar' \ibeatse[\prop] \ar$, thus, implies $¬ (\ar' \nibeatsst[\prop] \ar)$. But out of $¬ (\ar' (□\ibeatse[\prop]) \ar)$, nothing.
	\item Partition (objectively) $\allargs$ (or $\allargs × \alltopic$) into arguments in favor of $\prop, \text{sure}$, $¬\prop, \text{sure}$, and similarly for possible. Use only one rel $\ibeatse$, defined on contradictory arguments only, instead of $\ibeatse[\prop, \text{sure}]$ and others. Define $\ar' \ibeatse[\prop] \ar$ equals no when $¬(\ar' \ileadsto ¬\prop, \text{sure})$, equals $\ibeatse$ for adequate arguments, and equals yes when $¬(\ar \ileadsto \prop, \text{possible})$ and $\ar' \ileadsto ¬\prop, \text{sure}$, with probably some complications needed for the argument $\emptyset$ (and related default attitude towards $\prop$).
\end{itemize}
